Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-03-06 awipev-CO2.Rmd
seaFET's deployment periods changed

@@

# We decided to calibrate pH data within each pH spectro measurement.
# Thus, each pH spectro is taken as one calibration periode. 
# We calculate here the day between 2 pH spectro in order to have the start/end of one deployment period.
sfPeriod <- d_all%>%
  dplyr::select(datetime, pH_s_seafet_temp_field)%>%
  dplyr::filter(!is.na(pH_s_seafet_temp_field))
# Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
sfPeriod <- sfPeriod%>%
dplyr::filter(datetime != "2018-04-16 07:00:00" & datetime != "2018-12-14 09:00:00" & datetime != "2019-01-18 09:00:00")

sfPeriod <-  sfPeriod %>%
  dplyr::arrange(datetime) %>%
  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600)))%>%
  dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])

#put interval in a list with the start date of seaFET measurements
sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
#Change period sfinterv[5]. make the end of this period longer until 2018-03-21 23:59:00 
# This is needed in order to take in consideration pH from March 2018 with a calibration E0 lower (-1.4) than the next period (-0.38).
sfinterv[5] <- ymd_hms("2018-03-22 23:59:59")
#  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
#  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")

#sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# set deployment period between 2 spectro measurements.
# add here the new periods sfinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01, 
                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02, 
                                ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
                                ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
                                ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
                                ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
                                ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07,
                                ifelse(datetime >= sfinterv[8] & datetime <= sfinterv[9], 08,
                                ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
                                ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 10,
                                ifelse(datetime >= sfinterv[11] & datetime <= sfinterv[12], 11,
                                 ifelse(datetime >= sfinterv[12] & datetime <= sfinterv[13], 12,
                                 ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,
                                 ifelse(datetime >= sfinterv[14] & datetime <= sfinterv[15], 14,
                                 ifelse(datetime >= sfinterv[15] & datetime <= sfinterv[16], 15,
                                 ifelse(datetime >= sfinterv[16] & datetime <= sfinterv[17], 16,
                                 ifelse(datetime >= sfinterv[17] & datetime <= sfinterv[18], 17,
                                ifelse(datetime >= sfinterv[18] & datetime <= sfinterv[19], 18,
                                ifelse(datetime >= sfinterv[19] & datetime <= sfinterv[20], 19,
                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[21], 20,
                                ifelse(datetime >= sfinterv[21] & datetime <= sfinterv[22], 21,
                                #ifelse(datetime >= sfinterv[22] & datetime <= sfinterv[23], 22,
                                #ifelse(datetime >= sfinterv[23] & datetime <= sfinterv[24], 23,
                                #ifelse(datetime >= sfinterv[24] & datetime <= sfinterv[25], 24,
                                #ifelse(datetime >= sfinterv[25] & datetime <= sfinterv[26], 25,
                                ifelse(datetime >= sfinterv[22] , 22,NA )))))))))))))))))))))))

@@

# period 2, mean of 4 next hours for volt int + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-09-28 15:00:00" & datetime <= "2017-09-28 18:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2017-09-28 13:00:00" , mean_voltINT_4h, voltINT))

@@

# period 20, mean of 4 previous hours for volt int + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 04:00:00" & datetime <= "2019-09-13 07:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 08:00:00" , mean_voltINT_4h, voltINT))

@@

# period 21, mean of 4 previous hours for volt int + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 13:00:00" , mean_voltINT_4h, voltINT))

@@

  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[22], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@ 
# seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb,pHint_tot_sf)
# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
#   dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
#     dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
#     dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
#   dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
# 
#   dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
#   dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
#     dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
#   dyLegend(show = "auto")   %>%
#   dyAxis( "y2",valueRange = c(-3, 36))%>%
#   dyAxis( "y",valueRange = c(-2, 2))%>%
#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
#   dyRangeSelector(height = 30, dateWindow= NULL)
# # #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@

>>>>

We decided to change the calculation of E0. Before E0 was calculated for each pH spectro measurements. Now, EO is calculated making a mean of several E0 that come from one deployment period (sensor in the water for several months).

@@

# # We decided to calibrate pH data within each pH spectro measurement.
# # Thus, each pH spectro is taken as one calibration periode. 
# # We calculate here the day between 2 pH spectro in order to have the start/end of one deployment period.
# sfPeriod <- d_all%>%
#   dplyr::select(datetime, pH_s_seafet_temp_field)%>%
#   dplyr::filter(!is.na(pH_s_seafet_temp_field))
# # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
# sfPeriod <- sfPeriod%>%
# dplyr::filter(datetime != "2018-04-16 07:00:00" & datetime != "2018-12-14 09:00:00" & datetime != "2019-01-18 09:00:00")
# 
# sfPeriod <-  sfPeriod %>%
#   dplyr::arrange(datetime) %>%
#   dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600)))%>%
#   dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])
# 
# #put interval in a list with the start date of seaFET measurements
# sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
# #Change period sfinterv[5]. make the end of this period longer until 2018-03-21 23:59:00 
# # This is needed in order to take in consideration pH from March 2018 with a calibration E0 lower (-1.4) than the next period (-0.38).
# sfinterv[5] <- ymd_hms("2018-03-22 23:59:59")
# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# # sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# # sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
# 
# #sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# # set deployment period between 2 spectro measurements.

# # add here the new periods sfinterv[..]
# d_all <- d_all %>%
#   dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01, 
#                                 ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02, 
#                                 ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
#                                 ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
#                                 ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
#                                 ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
#                                 ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07,
#                                 ifelse(datetime >= sfinterv[8] & datetime <= sfinterv[9], 08,
#                                 ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
#                                 ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 10,
#                                 ifelse(datetime >= sfinterv[11] & datetime <= sfinterv[12], 11,
#                                  ifelse(datetime >= sfinterv[12] & datetime <= sfinterv[13], 12,
#                                  ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,
#                                  ifelse(datetime >= sfinterv[14] & datetime <= sfinterv[15], 14,
#                                  ifelse(datetime >= sfinterv[15] & datetime <= sfinterv[16], 15,
#                                  ifelse(datetime >= sfinterv[16] & datetime <= sfinterv[17], 16,
#                                  ifelse(datetime >= sfinterv[17] & datetime <= sfinterv[18], 17,
#                                 ifelse(datetime >= sfinterv[18] & datetime <= sfinterv[19], 18,
#                                 ifelse(datetime >= sfinterv[19] & datetime <= sfinterv[20], 19,
#                                 ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[21], 20,
#                                 ifelse(datetime >= sfinterv[21] & datetime <= sfinterv[22], 21,
#                                 #ifelse(datetime >= sfinterv[22] & datetime <= sfinterv[23], 22,
#                                 #ifelse(datetime >= sfinterv[23] & datetime <= sfinterv[24], 23,
#                                 #ifelse(datetime >= sfinterv[24] & datetime <= sfinterv[25], 24,
#                                 #ifelse(datetime >= sfinterv[25] & datetime <= sfinterv[26], 25,
#                                 ifelse(datetime >= sfinterv[22] , 22,NA )))))))))))))))))))))))

# set deployment period when seaFET is in/out of water
sfinterv <- c("2017-08-24 12:00:00","2018-04-17 12:00:00", "2019-09-02 12:00:00")

# add here the new periods sfinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01,
                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02,
                                ifelse(datetime >= sfinterv[3] , 03,NA ))))

@@

# period 1 also, mean of 4 next hours for volt int + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-09-28 15:00:00" & datetime <= "2017-09-28 18:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2017-09-28 13:00:00" , mean_voltINT_4h, voltINT))

@@

# period 03, mean of 4 previous hours for volt int + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 04:00:00" & datetime <= "2019-09-13 07:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 08:00:00" , mean_voltINT_4h, voltINT))

@@

# period 03 also, mean of 4 previous hours for volt int + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 13:00:00" , mean_voltINT_4h, voltINT))

@@

  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%

  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[22], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

# #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
    #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
  dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%

  dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
  dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
    dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyLegend(show = "auto")   %>%
  dyAxis( "y2",valueRange = c(-3, 36))%>%
  dyAxis( "y",valueRange = c(-2, 2))%>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
